---
title: "Raised Median Maps"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: yeti
    source_code: embed
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(leaflet, viridis, DT, flexdashboard)
devtools::install_github('rstudio/leaflet')
wd <- "C:\\Users\\m-plunkett\\Documents\\Projects\\Raised Median Maps\\"
setwd(wd)

# Load Places Objects from previous script run (1:13 is number of sites total)
sites <- 1:13
for (i in 1:length(sites)) {
  load(file=paste0("Site_",i,".Rdata"))
}

Site_1$Website <- paste0("<a href='",Site_1$Website,"' target='_blank'>",Site_1$Website,"</a>")
Site_2$Website <- paste0("<a href='",Site_2$Website,"' target='_blank'>",Site_2$Website,"</a>")
Site_3$Website <- paste0("<a href='",Site_3$Website,"' target='_blank'>",Site_3$Website,"</a>")
Site_4$Website <- paste0("<a href='",Site_4$Website,"' target='_blank'>",Site_4$Website,"</a>")
Site_5$Website <- paste0("<a href='",Site_5$Website,"' target='_blank'>",Site_5$Website,"</a>")
Site_6$Website <- paste0("<a href='",Site_6$Website,"' target='_blank'>",Site_6$Website,"</a>")
Site_7$Website <- paste0("<a href='",Site_7$Website,"' target='_blank'>",Site_7$Website,"</a>")
Site_8$Website <- paste0("<a href='",Site_8$Website,"' target='_blank'>",Site_8$Website,"</a>")
Site_9$Website <- paste0("<a href='",Site_9$Website,"' target='_blank'>",Site_9$Website,"</a>")
Site_10$Website <- paste0("<a href='",Site_10$Website,"' target='_blank'>",Site_10$Website,"</a>")
Site_11$Website <- paste0("<a href='",Site_11$Website,"' target='_blank'>",Site_11$Website,"</a>")
Site_12$Website <- paste0("<a href='",Site_12$Website,"' target='_blank'>",Site_12$Website,"</a>")
Site_13$Website <- paste0("<a href='",Site_13$Website,"' target='_blank'>",Site_13$Website,"</a>")

typepal1 <- colorFactor(rainbow(length(unique(Site_1$Main_Type))), Site_1$Main_Type)
typepal2 <- colorFactor(rainbow(length(unique(Site_2$Main_Type))), Site_2$Main_Type)
typepal3 <- colorFactor(rainbow(length(unique(Site_3$Main_Type))), Site_3$Main_Type)
typepal4 <- colorFactor(rainbow(length(unique(Site_4$Main_Type))), Site_4$Main_Type)
typepal5 <- colorFactor(rainbow(length(unique(Site_5$Main_Type))), Site_5$Main_Type)
typepal6 <- colorFactor(rainbow(length(unique(Site_6$Main_Type))), Site_6$Main_Type)
typepal7 <- colorFactor(rainbow(length(unique(Site_7$Main_Type))), Site_7$Main_Type)
typepal8 <- colorFactor(rainbow(length(unique(Site_8$Main_Type))), Site_8$Main_Type)
typepal9 <- colorFactor(rainbow(length(unique(Site_9$Main_Type))), Site_9$Main_Type)
typepal10 <- colorFactor(rainbow(length(unique(Site_10$Main_Type))), Site_10$Main_Type)
typepal11 <- colorFactor(rainbow(length(unique(Site_11$Main_Type))), Site_11$Main_Type)
typepal12 <- colorFactor(rainbow(length(unique(Site_12$Main_Type))), Site_12$Main_Type)
typepal13 <- colorFactor(rainbow(length(unique(Site_13$Main_Type))), Site_13$Main_Type)

knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```

Home
=====================================

### About this Site


This is a website to hold the maps created from the Google Places API retrieval. You can look at each map by clicking on the site name in the Maps navigation menu above. 


Links to Maps:

- [Site 1 - Koenig Ln]
- [Site 2 - FM 973]
- [Site 3 - Aquarena Springs Dr]
- [Site 4 - TX-80]
- [Site 5 - US-79/Palm Valley Blvd]
- [Site 6 - FM 620]
- [Site 7 - TX-29/University Ave]
- [Site 8 - FM 1460/AW Grimes Blvd]
- [Site 9 - FM 1431/Whitestone Blvd]
- [Site 10 - FM 1431/Whitestone Blvd]
- [Site 11 - FM 1431/Whitestone Blvd]
- [Site 12 - FM 685]
- [Site 13 - FM 685]


Site 1 - Koenig Ln {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_1, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal1(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_1$Google_Maps_URL,"' target='_blank'>",Site_1$Name,"</a></b>"),
                                  Site_1$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_1$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_1$Name)) %>%
  addLegend("bottomright", pal = typepal1, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_1[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 2 - FM 973 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_2, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal2(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_2$Google_Maps_URL,"' target='_blank'>",Site_2$Name,"</a></b>"),
                                  Site_2$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_2$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_2$Name)) %>%
  addLegend("bottomright", pal = typepal2, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_2[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 3 - Aquarena Springs Dr {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_3, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal3(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_3$Google_Maps_URL,"' target='_blank'>",Site_3$Name,"</a></b>"),
                                  Site_3$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_3$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_3$Name)) %>%
  addLegend("bottomright", pal = typepal3, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_3[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 4 - TX-80 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_4, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal4(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_4$Google_Maps_URL,"' target='_blank'>",Site_4$Name,"</a></b>"),
                                  Site_4$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_4$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_4$Name)) %>%
  addLegend("bottomright", pal = typepal4, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_4[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 5 - US-79/Palm Valley Blvd {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_5, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal5(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_5$Google_Maps_URL,"' target='_blank'>",Site_5$Name,"</a></b>"),
                                  Site_5$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_5$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_5$Name)) %>%
  addLegend("bottomright", pal = typepal5, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_5[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 6 - FM 620 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_6, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal6(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_6$Google_Maps_URL,"' target='_blank'>",Site_6$Name,"</a></b>"),
                                  Site_6$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_6$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_6$Name)) %>%
  addLegend("bottomright", pal = typepal6, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_6[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 7 - TX-29/University Ave {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_7, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal7(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_7$Google_Maps_URL,"' target='_blank'>",Site_7$Name,"</a></b>"),
                                  Site_7$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_7$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_7$Name)) %>%
  addLegend("bottomright", pal = typepal7, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_7[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 8 - FM 1460/AW Grimes Blvd {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_8, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal8(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_8$Google_Maps_URL,"' target='_blank'>",Site_8$Name,"</a></b>"),
                                  Site_8$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_8$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_8$Name)) %>%
  addLegend("bottomright", pal = typepal8, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_8[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 9 - FM 1431/Whitestone Blvd {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_9, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal9(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_9$Google_Maps_URL,"' target='_blank'>",Site_9$Name,"</a></b>"),
                                  Site_9$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_9$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_9$Name)) %>%
  addLegend("bottomright", pal = typepal9, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_9[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 10 - FM 1431/Whitestone Blvd {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_10, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal10(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_10$Google_Maps_URL,"' target='_blank'>",Site_10$Name,"</a></b>"),
                                  Site_10$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_10$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_10$Name)) %>%
  addLegend("bottomright", pal = typepal10, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_10[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 11 - FM 1431/Whitestone Blvd {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_11, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal11(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_11$Google_Maps_URL,"' target='_blank'>",Site_11$Name,"</a></b>"),
                                  Site_11$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_11$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_11$Name)) %>%
  addLegend("bottomright", pal = typepal11, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_11[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```


Site 12 - FM 685 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_12, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal12(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_12$Google_Maps_URL,"' target='_blank'>",Site_12$Name,"</a></b>"),
                                  Site_12$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_12$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_12$Name)) %>%
  addLegend("bottomright", pal = typepal12, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_12[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```

Site 13 - FM 685 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_13, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", group = "Hybrid", attribution = "Google") %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal13(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_13$Google_Maps_URL,"' target='_blank'>",Site_13$Name,"</a></b>"),
                                  Site_13$Full_Address,
                                  paste0("<b>Place Type:</b> ",Site_13$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_13$Name)) %>%
  addLegend("bottomright", pal = typepal13, values = ~Main_Type, labels = "Business Type ", title = "Business Types", group = "Legend") %>%
  addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), overlayGroups = c("Legend"), options = layersControlOptions(collapsed = FALSE), position = c("topleft"))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_13[,c(1,8,10:11,6)], rownames = F, escape = FALSE)
```