---
title: "Raised Median Maps"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: yeti
    source_code: embed
---

```{r setup, include=FALSE}

# This website was created by Michelle Plunkett in December 2017. 
# Michelle is a Graduate Student Worker at the Texas A&M Transportation Institute.
# She is a Master of Public Affairs candidate (Class of 2018) at UT Austin's LBJ School of Public Affairs.
# Contact Information: mplunkett@utexas.edu

if (!require("pacman")) install.packages("pacman")
pacman::p_load(viridis, flexdashboard, knitr)
pacman::p_load_gh('rstudio/leaflet','bhaskarvk/leaflet.extras','rstudio/DT')
wd <- "C:\\Users\\Michelle\\Documents\\Projects\\Raised Median Maps\\"
setwd(wd)

# Load Places Objects from previous script run (1:13 is number of sites total)
sites <- 1:13
for (i in 1:length(sites)) {
  load(file=paste0(wd,"Site_",i,".Rdata"))
  tmp <- get(paste0("Site_",i))
  tmp$Website <- paste0("<a href='",tmp$Website,"' target='_blank'>",tmp$Website,"</a>")
  paltemp <- colorFactor(rainbow(length(unique(tmp$Main_Type))), tmp$Main_Type)
  nam <- paste0("Site_",i)
  nam2 <- paste0("typepal",i)
  assign(nam, tmp)
  assign(nam2, paltemp)
}

# Labels
labels <- c("Site 1 - Koenig Ln", 
            "Site 2 - FM 973", 
            "Site 3 - Aquarena Springs Dr", 
            "Site 4 - TX-80", 
            "Site 5 - US-79/Palm Valley Blvd", 
            "Site 6 - FM 620",
            "Site 7 - TX-29/University Ave",
            "Site 8 - FM 1460/AW Grimes Blvd",
            "Site 9 - FM 1431/Whitestone Blvd",
            "Site 10 - FM 1431/Whitestone Blvd",
            "Site 11 - FM 1431/Whitestone Blvd",
            "Site 12 - FM 685",
            "Site 13 - FM 685")

# Create html widgets for each site
for (i in 1:length(sites)) {
  # Create all leaflet maps
  tmp <- get(paste0("Site_",i))
  temppal <- get(paste0("typepal",i))
  tempmap <- leaflet(data = tmp, width = "100%") %>%
              addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", 
                       group = "Google", attribution = 'Google') %>%
              addTiles(urlTemplate = "http://mt0.google.com/vt/lyrs=y&hl=en&x={x}&y={y}&z={z}&s=Ga", 
                       group = "Hybrid", attribution = "Google") %>%
              addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
              addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~temppal(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  tmp$Google_Maps_URL,"' target='_blank'>",
                                  tmp$Name,"</a></b>"),
                                  tmp$Full_Address,
                                  paste0("<b>Place Type:</b> ",
                                         tmp$Main_Type),sep="<br/>"), 
                   label = ~as.character(tmp$Name),
                   group = "Markers") %>%
              addLegend("bottomright", 
                        pal = temppal, 
                        values = ~Main_Type, 
                        labels = "Business Type ", 
                        title = "Business Types", 
                        group = "Legend") %>%
              addLayersControl(baseGroups = c("Google", "Hybrid", "ESRI"), 
                               overlayGroups = c("Legend"), 
                               options = layersControlOptions(collapsed = FALSE), 
                               position = c("topleft")) %>%
              addScaleBar(position="bottomleft", options = scaleBarOptions(metric=F)) %>%
              addSearchFeatures(targetGroups = "Markers", 
                                options = searchFeaturesOptions(zoom=19, 
                                                                autoCollapse = TRUE, 
                                                                hideMarkerOnCollapse = TRUE)) %>%
              addFullscreenControl()
  nam <- paste0("Site_",i,"_Map")
  assign(nam, tempmap)
  
  # Create all datatables
  temptable <- datatable(tmp[,c(1,8,10:11,6)], 
          rownames = F, 
          escape = FALSE,
          extensions = c("Buttons"), 
          options = list(
            searchHighlight = TRUE,
            dom = "Bfrtip",
            buttons = list("colvis",
              list(extend = "collection",
              buttons = list(
                          list(extend = "csv", 
                               title = paste0(gsub("/", "-", labels[i]))),
                          list(extend = "excel", 
                               title = paste0(gsub("/", "-", labels[i]))),
                          list(extend = "pdf", 
                               title = paste0(gsub("/", "-", labels[i])),
                               orientation = "landscape")),
              text = "Download"
            ))
          ))
  nam2 <- paste0("Site_",i,"_Table")
  assign(nam2, temptable)
}

knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```

Home
=====================================

### About this Site


This is a website to hold the maps created from Google Places API retrievals. You can look at each map by clicking on the site name in the Maps navigation menu above or by selecting a site from the list below. 

- [Site 1 - Koenig Ln]
- [Site 2 - FM 973]
- [Site 3 - Aquarena Springs Dr]
- [Site 4 - TX-80]
- [Site 5 - US-79/Palm Valley Blvd]
- [Site 6 - FM 620]
- [Site 7 - TX-29/University Ave]
- [Site 8 - FM 1460/AW Grimes Blvd]
- [Site 9 - FM 1431/Whitestone Blvd]
- [Site 10 - FM 1431/Whitestone Blvd]
- [Site 11 - FM 1431/Whitestone Blvd]
- [Site 12 - FM 685]
- [Site 13 - FM 685]


```{r, echo = FALSE, eval = TRUE}
# Output the pages for each site (with map on top, datatable on bottom)
out = NULL
for (i in 1:length(sites)) {
                           
    a1 <- paste0("\n\n",labels[[i]]," {data-navmenu='Maps'} \n")
    a2 <- paste0("===================================== \n\n")
    a3 <- "### Instructions \n"
    a4 <- "Hover over a point to see the name of the business. Click a point to see its address and a link to the business's Google Maps page. \n\n"
    a5 <- "### Map {.no-title } \n"
    a6 <- "\n\n```{r, echo=FALSE,fig.height=7,fig.align='center'}\n" # start r chunk
    a7 <-  sprintf("\n Site_%d_Map", i)
    a8 <- "\n\n```\n\n" # end r chunk
    a9 <- "### Business Details \n"
    a10 <- "\n\n```{r cols.print=7, echo=FALSE}\n" # start r chunk
    a11 <- sprintf("\n Site_%d_Table", i)
    a12 <- "\n\n```\n\n" # end r chunk

  out <- c(out, knit_expand(text=paste0(a1, a2, a3, a4, a5, a6, a7, a8, a9, a10, a11, a12)))
}
```

`r paste(knit(text = out), collapse = '\n')`