---
title: "Raised Median Maps"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: yeti
    source_code: embed
---

```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(leaflet, viridis, DT, flexdashboard)
wd <- "C:\\Users\\m-plunkett\\Documents\\Projects\\Raised Median Maps\\"
setwd(wd)

# Load Places Objects from previous script run
sites <- 1:12
for (i in 1:length(sites)) {
  load(file=paste0("Site_",i,".Rdata"))
}

typepal1 <- colorFactor(rainbow(length(unique(Site_1$Main_Type))), Site_1$Main_Type)
typepal2 <- colorFactor(rainbow(length(unique(Site_2$Main_Type))), Site_2$Main_Type)
typepal3 <- colorFactor(rainbow(length(unique(Site_3$Main_Type))), Site_3$Main_Type)
typepal4 <- colorFactor(rainbow(length(unique(Site_4$Main_Type))), Site_4$Main_Type)
typepal5 <- colorFactor(rainbow(length(unique(Site_5$Main_Type))), Site_5$Main_Type)
typepal6 <- colorFactor(rainbow(length(unique(Site_6$Main_Type))), Site_6$Main_Type)
typepal7 <- colorFactor(rainbow(length(unique(Site_7$Main_Type))), Site_7$Main_Type)
typepal8 <- colorFactor(rainbow(length(unique(Site_8$Main_Type))), Site_8$Main_Type)
typepal9 <- colorFactor(rainbow(length(unique(Site_9$Main_Type))), Site_9$Main_Type)
typepal10 <- colorFactor(rainbow(length(unique(Site_10$Main_Type))), Site_10$Main_Type)
typepal11 <- colorFactor(rainbow(length(unique(Site_11$Main_Type))), Site_11$Main_Type)
typepal12 <- colorFactor(rainbow(length(unique(Site_12$Main_Type))), Site_12$Main_Type)

knitr::opts_chunk$set(echo = TRUE, fig.align="center")
```

Home
=====================================

### About this Site


This is a website to hold the maps created from the Google Places API retrieval. You can look at each map by clicking on the site name in the Maps navigation menu above. 


Links to Maps:

- [Site 1 - Koenig Ln]
- [Site 2 - FM 973]
- [Site 3 - Aquarena Springs Dr]
- [Site 4 - TX-80]
- [Site 5 - US-79/Palm Valley Blvd]
- [Site 6 - FM 620]
- [Site 7 - TX-29/University Ave]
- [Site 8 - FM 1460/A.W. Grimes Blvd]
- [Site 9 - FM 1431/Whitestone]
- [Site 10 - FM 1431/Whitestone]
- [Site 11 - FM 685]
- [Site 12 - FM 685]


Site 1 - Koenig Ln {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_1, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal1(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_1$Google_Maps_URL,"' target='_blank'>",Site_1$Name,"</a></b>"),
                                  Site_1$Full_Address,
                                  paste0("Place Type: ",Site_1$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_1$Name)) %>%
  addLegend("bottomright", pal = typepal1, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_1[,c(1,8,6)], rownames = F)
```

Site 2 - FM 973 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_2, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal2(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_2$Google_Maps_URL,"' target='_blank'>",Site_2$Name,"</a></b>"),
                                  Site_2$Full_Address,
                                  paste0("Place Type: ",Site_2$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_2$Name)) %>%
  addLegend("bottomright", pal = typepal2, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_2[,c(1,8,6)], rownames = F)
```

Site 3 - Aquarena Springs Dr {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_3, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal3(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_3$Google_Maps_URL,"' target='_blank'>",Site_3$Name,"</a></b>"),
                                  Site_3$Full_Address,
                                  paste0("Place Type: ",Site_3$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_3$Name)) %>%
  addLegend("bottomright", pal = typepal3, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_3[,c(1,8,6)], rownames = F)
```

Site 4 - TX-80 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_4, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal4(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_4$Google_Maps_URL,"' target='_blank'>",Site_4$Name,"</a></b>"),
                                  Site_4$Full_Address,
                                  paste0("Place Type: ",Site_4$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_4$Name)) %>%
  addLegend("bottomright", pal = typepal4, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_4[,c(1,8,6)], rownames = F)
```

Site 5 - US-79/Palm Valley Blvd {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_5, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal5(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_5$Google_Maps_URL,"' target='_blank'>",Site_5$Name,"</a></b>"),
                                  Site_5$Full_Address,
                                  paste0("Place Type: ",Site_5$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_5$Name)) %>%
  addLegend("bottomright", pal = typepal5, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_5[,c(1,8,6)], rownames = F)
```

Site 6 - FM 620 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_6, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal6(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_6$Google_Maps_URL,"' target='_blank'>",Site_6$Name,"</a></b>"),
                                  Site_6$Full_Address,
                                  paste0("Place Type: ",Site_6$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_6$Name)) %>%
  addLegend("bottomright", pal = typepal6, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_6[,c(1,8,6)], rownames = F)
```

Site 7 - TX-29/University Ave {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_7, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal7(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_7$Google_Maps_URL,"' target='_blank'>",Site_7$Name,"</a></b>"),
                                  Site_7$Full_Address,
                                  paste0("Place Type: ",Site_7$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_7$Name)) %>%
  addLegend("bottomright", pal = typepal7, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_7[,c(1,8,6)], rownames = F)
```

Site 8 - FM 1460/A.W. Grimes Blvd {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_8, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal8(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_8$Google_Maps_URL,"' target='_blank'>",Site_8$Name,"</a></b>"),
                                  Site_8$Full_Address,
                                  paste0("Place Type: ",Site_8$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_8$Name)) %>%
  addLegend("bottomright", pal = typepal8, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_8[,c(1,8,6)], rownames = F)
```

Site 9 - FM 1431/Whitestone {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_9, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal9(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_9$Google_Maps_URL,"' target='_blank'>",Site_9$Name,"</a></b>"),
                                  Site_9$Full_Address,
                                  paste0("Place Type: ",Site_9$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_9$Name)) %>%
  addLegend("bottomright", pal = typepal9, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_9[,c(1,8,6)], rownames = F)
```

Site 10 - FM 1431/Whitestone {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_10, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal10(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_10$Google_Maps_URL,"' target='_blank'>",Site_10$Name,"</a></b>"),
                                  Site_10$Full_Address,
                                  paste0("Place Type: ",Site_10$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_10$Name)) %>%
  addLegend("bottomright", pal = typepal10, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_10[,c(1,8,6)], rownames = F)
```

Site 11 - FM 685 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_11, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal11(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_11$Google_Maps_URL,"' target='_blank'>",Site_11$Name,"</a></b>"),
                                  Site_11$Full_Address,
                                  paste0("Place Type: ",Site_11$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_11$Name)) %>%
  addLegend("bottomright", pal = typepal11, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_11[,c(1,8,6)], rownames = F)
```

Site 12 - FM 685 {data-navmenu="Maps"}
=====================================

### Instructions

Hover over a point to see the the name of the business. Click on a point to reveal a pop-up with its address and a link to the business's Google Maps webpage.


### Map {.no-title }

```{r, echo=FALSE,fig.height=8,fig.align="center"}
leaflet(data = Site_12, width = "100%") %>%
  addTiles(urlTemplate = "https://mts1.google.com/vt/lyrs=s&hl=en&src=app&x={x}&y={y}&z={z}&s=G", group = "Google", attribution = 'Google') %>%
  addProviderTiles("Esri.WorldImagery", group = "ESRI") %>%
  addCircleMarkers(~Longitude, ~Latitude, 
                   radius=9, 
                   fillColor = ~typepal12(Main_Type), 
                   stroke=T, color = "#FFFFFF", opacity = 0.8, fillOpacity = 0.9, 
                   popup = ~paste(paste0("<b><a href='",
                                  Site_12$Google_Maps_URL,"' target='_blank'>",Site_12$Name,"</a></b>"),
                                  Site_12$Full_Address,
                                  paste0("Place Type: ",Site_12$Main_Type),sep="<br/>"), 
                   label = ~as.character(Site_12$Name)) %>%
  addLegend("bottomright", pal = typepal12, values = ~Main_Type, labels = "Business Type ", title = "Business Types") %>%
  addLayersControl(baseGroups = c("Google", "ESRI"), options = layersControlOptions(collapsed = FALSE))
```


### Business Details

```{r cols.print=7, rows.print=54, echo=FALSE}
datatable(Site_12[,c(1,8,6)], rownames = F)
```